---
title: "Untitled"
author: "Ryan Quinn"
date: "February 2, 2021"
output: html_document
---
 
-Isolate grassland data
-Cut off any depths below 1 meter 
```{r}
df.g <- subset(df, df$type == "grassland")
df.g <- subset(df.g, depth == 0 | depth == 10 | depth == 20 | depth == 30 | depth == 40 | depth == 50 | depth == 60 | depth == 70 | depth == 80 | depth == 90) #only interested in top 100cm
```

-Look at summary stats for each depth distribution 
```{r}
grass <- df.g %>% group_by(depth) %>% summarize(mean = mean(as.numeric(rb)), 
                                    se = se.error(rb), 
                                    n = length(rb))
```
*N is only >20 for the first three depth distributions.

-Use lm() to explore 
```{r}
df.g <- subset(df.g, !is.na(df.g$rb)) #remove where we don't know plant type 
grass.rb <- lm(log(rb)~as.factor(depth), data=df.g) 
summary(grass.rb)
anova(grass.rb)
emmeans:: emmeans(grass.rb, pairwise ~ depth)

plot(log(df.g$rb) ~ df.g$depth) #very clear decline in FRB with increasing soil depth 
```

-Grassland nitrogen deposition plot (Since replication is not great below 30cm, we will only use the surface soil layers to attempt to identify relationships between FRB and nitrogen deposition.)
```{r}
iso0 <- subset(df.g, df.g$depth == 0)
line0 <- (lm(log(iso0$rb) ~ as.numeric(iso0$ndep)))

iso10 <- subset(df.g, df.g$depth == 10)
line10 <- (lm(log(iso10$rb) ~ as.numeric(iso10$ndep)))

iso20 <- subset(df.g, df.g$depth == 20)
line20 <- (lm(log(iso20$rb) ~ as.numeric(iso20$ndep)))

plot(log(df.g$rb[df.g$depth == 0]) ~  df.g$ndep[df.g$depth == 0], pch=19, type="p")
abline(line0)
lines(log(df.g$rb[df.g$depth == 10]) ~  df.g$ndep[df.g$depth == 10], col="green", pch=19, type="p")
abline(line10, col="green")
lines(log(df.g$rb[df.g$depth == 20]) ~  df.g$ndep[df.g$depth == 20], col="blue", pch=19, type="p")
abline(line20, col="blue")
legend("bottomright", col=c("black", "green", "blue"), c("0-10", "10-20", "20-30"), pch=19, lty=1, lwd=2)
```

-Use lm() to explore 
```{r}
df.gn <- subset(df.g, df.g$depth < 40)
grass.rb.gn <- lm(log(rb)~as.factor(depth) * as.numeric(ndep), data=df.gn) 
anova(grass.rb.gn)
summary(grass.rb.gn) 
```

Other Interesting plots: 

-Grassland MAT plot
```{r}
iso0 <- subset(df.g, df.g$depth == 0)
line0 <- (lm(log(iso0$rb) ~ as.numeric(iso0$map)))

iso10 <- subset(df.g, df.g$depth == 10)
line10 <- (lm(log(iso10$rb) ~ as.numeric(iso10$map)))

iso20 <- subset(df.g, df.g$depth == 20)
line20 <- (lm(log(iso20$rb) ~ as.numeric(iso20$map)))

plot(log(df.g$rb[df.g$depth == 0]) ~  df.g$map[df.g$depth == 0], pch=19, type="p")
abline(line0)
lines(log(df.g$rb[df.g$depth == 10]) ~  df.g$map[df.g$depth == 10], col="green", pch=19, type="p")
abline(line10, col="green")
lines(log(df.g$rb[df.g$depth == 20]) ~  df.g$map[df.g$depth == 20], col="blue", pch=19, type="p")
abline(line20, col="blue")
legend("bottomright", col=c("black", "green", "blue"), c("0-10", "10-20", "20-30"), pch=19, lty=1, lwd=2)
```

-Grassland MAT plot
```{r}
iso0 <- subset(df.g, df.g$depth == 0)
line0 <- (lm(log(iso0$rb) ~ as.numeric(iso0$mat)))

iso10 <- subset(df.g, df.g$depth == 10)
line10 <- (lm(log(iso10$rb) ~ as.numeric(iso10$mat)))

iso20 <- subset(df.g, df.g$depth == 20)
line20 <- (lm(log(iso20$rb) ~ as.numeric(iso20$mat)))

plot(log(df.g$rb[df.g$depth == 0]) ~  df.g$mat[df.g$depth == 0], pch=19, type="p")
abline(line0)
lines(log(df.g$rb[df.g$depth == 10]) ~  df.g$mat[df.g$depth == 10], col="green", pch=19, type="p")
abline(line10, col="green")
lines(log(df.g$rb[df.g$depth == 20]) ~  df.g$mat[df.g$depth == 20], col="blue", pch=19, type="p")
abline(line20, col="blue")
legend("bottomright", col=c("black", "green", "blue"), c("0-10", "10-20", "20-30"), pch=19, lty=1, lwd=2)
```