---
title: "Untitled"
author: "Ryan Quinn"
date: "April 22, 2020"
output: html_document
---
```{r}
source("C:/Users/nobody/Documents/R/MyScript.R")
```

-Mean +/- SE FRB along a soil depth increment gradient in forests across North America 
```{r}
forest$source <- "forest"

ggplot(forest, aes(x=as.factor(depth), y=mean))+
  geom_col(position="dodge", stat="identity", fill = "dodgerblue4")+theme_classic(base_size=13)+labs(title="forest")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="black", width=.4, position=pd)+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression(root~biomass~(g/m^2), breaks=seq(0,500,100)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))#+geom_text(aes(label = n, y = mean), size = 5, face="bold", color="red", vjust=4)

```



-Mean +/- SE FRB along a soil depth increment gradient in grasslands across North America 
```{r}
grass$source <- "grassland"

ggplot(grass, aes(x=as.factor(depth), y=mean))+
  geom_col(position="dodge", stat="identity", fill = "forestgreen")+theme_classic(base_size=13)+labs(title="grassland")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="black", width=.4, position=pd)+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression(root~biomass~(g/m^2), breaks=seq(0,500,100)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))#geom_text(aes(label = mean, y ), size = 5, face="bold", color="red", vjust=-0.98)


```

-Mean +/- SE FRB along a soil depth increment gradient in shrublands across North America 
```{r}
shrub$source <- "shrubs"

ggplot(shrub, aes(x=as.factor(depth), y=mean))+
  geom_col(position="dodge", stat="identity", fill = "goldenrod")+theme_classic(base_size=13)+labs(title="shrub")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="black", width=.4, position=pd)+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression(root~biomass~(g/m^2), breaks=seq(0,500,100)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))#+geom_text(aes(label = n, y = mean), size = 5, face="bold", color="red", vjust=-1.3)
```

-Figure showing mean FRB for each depth increment for each plant type +/- SE 
```{r}
all <- rbind(forest, grass, shrub)
ggplot(all, aes(x=as.factor(depth), y=mean, fill=as.factor(source)))+
  geom_col(position="dodge")+theme_classic(base_size=13)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="black", width=.4, position=pd)+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression(root~biomass~(g/m^2), breaks=seq(0,500,100)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+scale_fill_manual(values=c("dodgerblue4", "forestgreen", "goldenrod"))
```




-Plots which show sample size for each depth increment for each plant class 
```{r}
ggplot(forest, aes(x=as.factor(depth), y=n))+
  geom_col(position="dodge", stat="identity", fill = "dodgerblue4")+theme_classic(base_size=13)+labs(title="forest")+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression("sample size", breaks=seq(0,500,50)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+geom_text(aes(label = n, y = n), size = 5, face="bold", color="red", vjust=1.5)

ggplot(grass, aes(x=as.factor(depth), y=n))+
  geom_col(position="dodge", stat="identity", fill = "forestgreen")+theme_classic(base_size=13)+labs(title="grassland")+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression("sample size", breaks=seq(0,500,50)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+geom_text(aes(label = n, y = n), size = 5, face="bold", color="red", vjust=1.5)

ggplot(shrub, aes(x=as.factor(depth), y=n))+
  geom_col(position="dodge", stat="identity", fill = "goldenrod")+theme_classic(base_size=13)+labs(title="shrub")+
  scale_x_discrete("depth (cm)", labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100"), expand = c(0,0))+theme(axis.text.x = element_text(angle = 45, hjust = 1))+scale_y_continuous(expand = c(0,0), expression("sample size", limits=c(0,300)))+theme(legend.title = element_text(color = "black", size = 11, face="bold"), legend.text = element_text(color = "black", size=10))+ theme(legend.title.align=0.5)+labs(fill="plant type")+ theme(axis.text = element_text(size=12))+theme(axis.title.x = element_text(margin = unit(c(5, 0, 0, 0), "mm")))+theme(axis.title.y = element_text(size=14, face="bold"))+theme(axis.title.x = element_text(size=14, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+theme(plot.title = element_text(hjust=0.5, size=20, face="bold"))+geom_text(aes(label = n, y = n), size = 5, face="bold", color="red", vjust=1.5)
```